Supplementary Information

### 2021-04-27 doc/manuscript/Dow_SI.Rmd
remove sample size by species tables
#51

#SI table captions
species_table_caption <-"Table S1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes analyzed here."
sample_size_by_species_caption <-"Table EXTRA | Dendrometer band sample size by species at SCBI and HF. TO BE REMOVED"
sample_size_by_year_caption <- "Table S2 | Sample size by year "
mean_growth_parameters_caption = "Table S3 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. "

@@

```{r, Table SCBI_bands_bySP, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
table <- read.csv("tables_figures/SCBI_bands_bySP.csv",stringsAsFactors = FALSE, check.names = FALSE)
kbl(table, caption = sample_size_by_species_caption , format = "latex", booktabs = T) %>%
  kable_styling(latex_options = "hold_position")
```

```{r, Table HF_bands_bySP, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
table <- read.csv("tables_figures/HF_bands_bySP.csv",stringsAsFactors = FALSE, check.names = FALSE)
kbl(table, caption = sample_size_by_species_caption, format = "latex", booktabs = T) %>%
  kable_styling(latex_options = "hold_position")
```

*These tables overlap with the species table, and probably is not necessary. They also do not match-- probably out of date.*

>>>>

#SI table captions
species_table_caption <-"Table S1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
sample_size_by_year_caption <- "Table S2 | Sample size by year "
mean_growth_parameters_caption = "Table S3 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. "

@@

### 2021-04-27 doc/manuscript/Dow_manuscript_Nature.Rmd
remove sample size by species tables
#51

# SUPPLEMENTARY INFO (this chunk must be repeated in Dow_SI.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_species= "S2"
sample_size_by_year= "S2"
mean_growth_parameters_table="S3" 
chronologies_table="S4" #!!! Hand-numbered in tree-ring figure captions

>>>>

# SUPPLEMENTARY INFO (this chunk must be repeated in Dow_SI.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_year= "S2"
mean_growth_parameters_table="S3" 
chronologies_table="S4" #!!! Hand-numbered in tree-ring figure captions
